Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-04-30 ms.tex
prescription for Fourier amplitude

The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 44.4$\degree$ and 67.8$\degree$, close to the observed crosshatch angles.
We therefore conclude that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.

>>>>

The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 44.4$\degree$ and 67.8$\degree$, close to the observed crosshatch angles.
We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.

The crosshatch structure of the detectors extends down to the subpixel level, so it will not be fully corrected with a flat field division.
This sub-pixel structure has been imaged with microscopy on a Euclid HgCdTe detector \citep{shapiro2018crosshatch}.
The width of the structures can be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
We estimate that the crosshatch pattern oriented at 90.9$\degree$ crosses 1 horizontal pixel for every 64 vertical pixels.
While crossing the boundary, there are $\approx 38$ rows where the crosshatch pattern spans more than 2 pixels.
If the crosshatch pattern has a tophat response function, then these 38 rows where the pattern spans two pixels imply a tophat full width of 0.6 pixels or a physical width of 10.8~$\mu$m for an 18~$\mu$m pixel pitch.
This is more than twice the estimate from \citet{ninan2019crosshatchHPF} for an HgCdTe used on the Habitable Planet Finder.
It is possible that the crosshatch pattern's width varies among detectors or that a tophat function is a poor approximation of the actual subpixel response.
Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.

We attempt to model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency.
We model the two dimensional Fourier amplitude $f(x',y')$ for one angle as
\begin{equation}
f(x',y') = \exp{\left(-y'^2/\tau_\perp\right)} \left( \frac{a}{b + x'^2} + \frac{c}{1 + \exp{\left( (|x'| - d)/\tau_\parallel \right)} } \right),
\end{equation}
where $x'$ and $y'$ are rotated coordinates, $\tau_\perp$ is the perpendicular exponential constant, $a$ and $b$ are polynomial constants for the central peak of the Fourier plane, $c$ is an exponential amplitude constant and $d$ is the cutoff frequency with an exponential constant $\tau_\parallel$.
For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
\begin{equation}
x' = (x - x_0) \cos{\theta} + (y - y_0) \sin{\theta}
\end{equation}
and
\begin{equation}
y' = -(x - x_0) \sin{\theta} + (y - y_0) \cos{\theta}.
\end{equation}
We include three angles so that the total Fourier amplitude is
\begin{equation}
f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i,y'_i)
\end{equation}
for $\theta_i = 0.9^\circ$, 68.7$^\circ$ and 113.2$^\circ$.
